Honey Bees - DESeq

### 2018-04-16 NC_NR_VC_VR/DESeq2/Method1/makeDataMetrics.Rmd
Grep linux scripts for GOs

    t1Length <- length(which(metrics[which(metrics$padj <0.05),]$log2FoldChange>0))
    t2Length <- length(which(metrics[which(metrics$padj <0.05),]$log2FoldChange<0))

>>>>

    sigMet <- metrics[which(metrics$padj <0.05),]
    t1Length <- length(which(sigMet$log2FoldChange>0))
    t2Length <- length(which(sigMet$log2FoldChange<0))

    saveRDS(sigMet[which(sigMet$log2FoldChange>0),]$ID, file=paste0(uTreat[i], "_", uTreat[j], "_", uTreat[i], ".Rds"))
    saveRDS(sigMet[which(sigMet$log2FoldChange<0),]$ID, file=paste0(uTreat[i], "_", uTreat[j], "_", uTreat[j], ".Rds"))
